### 2018-02-14 README.Rmd
update contribs in readme, add a few more ctb people in DESCRIPTION file

+ [Ignasi Bartomeus](https://github.com/ibartomeus)
+ [John Baumgartner](https://github.com/johnbaums)
+ [Carl Boettiger](https://github.com/cboettig)
+ [Joseph Brown](https://github.com/josephwb)
+ [Scott Chamberlain](https://github.com/sckott)
+ [Anirvan Chatterjee](https://github.com/anirvan)
+ [Zachary Foster](https://github.com/zachary-foster)
+ [Oliver Keyes](https://github.com/Ironholds)
+ [David LeBauer](https://github.com/dlebauer)
+ [Philippe Marchand](https://github.com/pmarchand1)
+ [Ben Marwick](https://github.com/benmarwick)
+ [Francois Michonneau](https://github.com/fmichonneau)
+ [James O'Donnell](https://github.com/jimmyodonnell)
+ [Jari Oksanen](https://github.com/jarioksa)
+ [Karthik Ram](https://github.com/karthik)
+ [raredd](https://github.com/raredd)
+ [Eduard Szöcs](https://github.com/EDiLD)
+ [Luis Villanueva](https://github.com/ljvillanueva)
+ [Jakub Wilk](https://github.com/jwilk)

@@

>>>>

+ [Zebulun Arendsee](https://github.com/arendsee)
+ [Ignasi Bartomeus](https://github.com/ibartomeus)
+ [John Baumgartner](https://github.com/johnbaums)
+ [Carl Boettiger](https://github.com/cboettig)
+ [Joseph Brown](https://github.com/josephwb)
+ [Scott Chamberlain](https://github.com/sckott)
+ [Anirvan Chatterjee](https://github.com/anirvan)
+ [Zachary Foster](https://github.com/zachary-foster)
+ [Patrick Hausmann](https://github.com/patperu)
+ [Oliver Keyes](https://github.com/Ironholds)
+ [David LeBauer](https://github.com/dlebauer)
+ [Philippe Marchand](https://github.com/pmarchand1)
+ [Ben Marwick](https://github.com/benmarwick)
+ [Francois Michonneau](https://github.com/fmichonneau)
+ [James O'Donnell](https://github.com/jimmyodonnell)
+ [Jari Oksanen](https://github.com/jarioksa)
+ [Karthik Ram](https://github.com/karthik)
+ [raredd](https://github.com/raredd)
+ [Alexey Shiklomanov](https://github.com/ashiklom)
+ [Eduard Szöcs](https://github.com/EDiLD)
+ [Vinh Tran](https://github.com/trvinh)
+ [Bastian Greshake Tzovaras](https://github.com/gedankenstuecke)
+ [Luis Villanueva](https://github.com/ljvillanueva)
+ [Jakub Wilk](https://github.com/jwilk)

@@

[![rofooter](https://ropensci.org/public_images/github_footer.png)](https://ropensci.org)
